Covid-19 A Spatio-Temporal Investigation.

### 2021-01-11 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 The prospective scan statistic proposed by Kulldorff $\!\!^5$ was chosen to identify emerging spatio-temporal *clusters* in the cumulative number of cases for each month, to apply the technique it was considered that the data follows a Poisson distribution. The purely spatial scan statistics $\!\!^1\!^1$, creates a wide variety of circular windows in different locations throughout the map, each one with a specific group of neighboring areas, all of these circular windows are also flexible in its two dimensions, size and locality, and may or not contain a *cluster* of events
...

  cria várias janelas circulares em diversas localidades no mapa, cada uma com diferentes grupos de áreas vizinhas, sendo cada uma dessas janelas circulares flexíveis em suas duas dimensões de tamanho e localidade, podendo ou não conter um *cluster* de eventos. A estatística de scan é definida como a razão de verossimilhança sobre todos os possíveis círculos e ao ser maximizada identifica o que constitui o *cluster* mais provável, o *p*-valor é obtido pelo teste de hipótese de *Monte-Carlo*.

>>>>

  The prospective scan statistic proposed by Kulldorff $\!\!^5$ was chosen to identify emerging spatio-temporal *clusters* in the cumulative number of cases for each month, to apply the technique it was considered that the data follows a Poisson distribution. The purely spatial scan statistic $\!\!^1\!^1$ creates a wide variety of circular windows in different locations throughout the map, each one with a specific group of neighboring areas, all of these circular windows are also flexible in their two dimensions, size and locality, and may or not contain a *cluster* of events. A scan statistic is defined as the likelihood ratio over all possible circles and when maximized identifies the one which constitutes the most likely *cluster*, the *p*-value is obtained through the *Monte-Carlo* hypothesis test.
